A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-28 sections/Discussion.tex
S5.3 Elaboration

\subsection{Scoped type variables}

\subsection{Elaboration}

OTHERS?

>>>>

% \subsection{Scoped type variables} Not discussed for this paper

%-------------------------------------------------------------------------------
\subsection{Elaboration}
While our algorithmic reduction does not elaborate to System F,
it is not difficult to extend the algorithm with a type-directed translation.
Since the judgment form of our algorithmic worklist contains a collection of judgments,
elaboration expressions are also generated as a list of equal length to
the number of judgments (NOT judgment chains!) in the worklist.
Within expectation, subtyping judgments translate to type coercions (denoted by $f$),
all three other types of judgments translate to terms in System F (denoted by $t$).

Let $\Phi$ be the elaboration list, containing translated type coercions and terms:
$$\Phi ::= \nil \mid \Phi, f \mid \Phi, t$$

And the form of our algorithmic judgment becomes:
$$\Gamma \hookrightarrow \Phi$$

We take Rule 18 as an example, rewritting small-step reduction into a relational style,
$$
\inferrule*[right=$\mathtt{Translation\_18}$]
{\Gamma \Vdash e \To_a a \le B \hookrightarrow \Phi, f, t}
{\Gamma \Vdash e \Lto B \hookrightarrow \Phi, f t}
$$
As is shown in the conclusion of the rule,
a checking judgment on the top of the worklist corresponds to a top element for elaboration.
The premise indicates that one judgment chain may relate to more than one elaboration elements,
and that the outer judgment, being processed before inner ones,
elaborates to the top element in the elaboration list.

Existential variables need special treatment, since they may be solved at any step,
or being recycled if not solved in its scope.
If an existential variable is solved, we not only propagate the solution to the rest judgments,
but also replace ocurrances in the elaboration list.
If an existential variable is recycled, meaning that it is not constraint,
we can pick any well-formed monotype as its solution.
The unit type $1$, as the simplest type in the system, is a good choice.
